msc dissertation

### 2021-08-20 index.Rmd
latest

---
title: "msc dissertation"
author: "Halleyson Li 200256823"
date: '''r Sys.Date()'''
output:
  html_document: default
  pdf_document: default
line-citations: apalike
linkcolor: blue
frontsize: 12pt
---

@@

Because the original data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file. But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv but not read.csv.

@@

#re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
###(06/08/21 update: realize I could do it after change it from wide to long, then only the column: "measurement" needs to perform the change.)

@@

##Try something new, see if it makes the results better

###Ordinal logistic regression (best to apply when using likert scale)
```{r, message=FALSE}
#Ordinal logistic regression

@@

ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + 
  geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All Subjects")

@@

ggplot(ggpredict_ordinaldata1, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 1 Screener Correct")

@@

ggplot(ggpredict_ordinaldata2, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 2 Screener Correct")

@@

ggplot(ggpredict_ordinaldata3, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5) + labs(title = "All 3 Screener Correct")

>>>>

---
title: "msc dissertation"
author: "200256823"
date: '''r Sys.Date()'''
output:
  html_document: default
  pdf_document: default
line-citations: apalike
linkcolor: blue
frontsize: 12pt
---

@@

Because the original data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file. But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv, not read.csv.

@@

#re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
##(06/08/21 update: realize I could do it after change it from wide to long, then only the column: "measurement" needs to perform the change, for documentation reason, I leave it as it is.)

@@

##Considering the likert scale should be treated as categorical rather than continuse, thus the ordinal logistic regression should be used, rather than normal linear regression

```{r, message=FALSE}
#Ordinal logistic regression

@@

ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All Subjects")

  + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) #this gives you the box label of each points

@@

ggplot(ggpredict_ordinaldata1, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "\u2265 1 Screener Correct")

 + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)

@@

ggplot(ggpredict_ordinaldata2, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing")  + labs(title = "\u2265 2 Screener Correct")

 + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)

@@

ggplot(ggpredict_ordinaldata3, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All 3 Screener Correct")

 + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5)
